---
title: "CSR Paper Results"
author: "Aneta Pintekova"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
```
##### Notes

* Results are shown with robust standard errors \
* Size measured as log(assets) only for now

---

# 1. Models with total CSR score

## a) Model for the whole period, RND not adjusted


```{r echo = FALSE}
all_results_overall_csr[[1]]
```

## b) Model for the old period (till 2016), RND not adjusted


```{r echo = FALSE}
all_results_overall_csr[[2]]
```

## c) Model for the full period, missing RND equal to zero 


```{r echo = FALSE}
all_results_overall_csr[[3]]
```

## d) Model for the full period, missing RND equal to industry average or percentage of revenues


```{r echo = FALSE}
all_results_overall_csr[[4]]
```

## e) Model for the full period, missing RND equal to percentage of revenues


```{r echo = FALSE}
all_results_overall_csr[[5]]
```


# 2. Models with primary and secondary CSR score

## a) Model for the whole period, RND not adjusted


```{r echo = FALSE}
all_results_prim_sec_csr[[1]]
```

## b) Model for the old period (till 2016), RND not adjusted


```{r echo = FALSE}
all_results_prim_sec_csr[[2]]
```

## c) Model for the full period, missing RND equal to zero 


```{r echo = FALSE}
all_results_prim_sec_csr[[3]]
```

## d) Model for the full period, missing RND equal to industry average or percentage of revenues


```{r echo = FALSE}
all_results_prim_sec_csr[[4]]
```

## e) Model for the full period, missing RND equal to percentage of revenues


```{r echo = FALSE}
all_results_prim_sec_csr[[5]]
```